HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-06-29 scnn.tex
update figures

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.32\textwidth]{figures/result_order1.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order2.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
\caption{Classification errors for the 3 different problems. \nati{TODO: order is not correct} }
\label{fig:results}
\end{figure*}

@@

Figure: Filters 1D and Gnonomic

>>>>

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.32\textwidth]{figures/result_order1.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order2.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
\caption{Classification errors for the 3 different problems.}
\label{fig:results}
\end{figure*}

@@

Figure: Filters 1D and Gnonomic
\begin{figure*}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/section_filter_last.pdf} 
\includegraphics[width=0.45\textwidth]{figures/gnonomic_filter_last.pdf}
\caption{24 learned filters selected from the last spherical convolutional layer. Left: section. Right: gnonomic view.}
\label{fig:learned_filter}
\end{figure*}
